Study on the effectiveness of the investment strategy based on a classifier with rules adapted by machine learning

### 2013-09-29 Article/Article20130912/LatexArt/tewi-paper-template_minipages.tex
research procedure

Figure ~\ref{research_methods} on page ~\pageref{research_methods} shows how the research was conducted. Knowing the historical data recoiled by 1000 candles and they used the approach described above in order to find optimal parameters for a given period. After the appointment of tests performed on the current data. The strategy of the learned parameters should be used as long as it will bring satisfactory results on new data. When results are no longer good enough, the following parameters for the re-designation of historical data. Thus, the authors aim is to determine the point where it should be re- conversion parameters. Additionally, the authors set out to test a new standard of quality prediction. Now, extending the period of testing can produce better results, but more slowly or can not slip out of the local capital than some initial period, when the classic "remembers" the nature of the market. This new criterion is profit attributable to one candle variable of the test period.\\

>>>>

Figure ~\ref{research_methods} on page ~\pageref{research_methods} shows how the research was conducted. Knowing the historical data 1000 candles were used and approach described above in order to find optimal parameters for a given period was used for this dataset. After the parameters search, tests were performed on the current data. The strategy for the learned parameters should be used as long as it will bring satisfactory results on new data. When results were no longer good enough, the next parameters search were performed on next piece of historical data. Thus, the authors aim is to determine the point where it should parameters be recalculated. Additionally, the authors set out to test a new standard of quality prediction. Now, extending the period of testing can produce better results, but more slowly or with local drawndown in comparision to first period, when the classifier "remembers" the nature of the market. This new criteria is profit attributable to one candle of the testing period.\\
